### 2023-09-13 main.tex
asd

Since $Q^{2L}$ and $H^{''}$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with the above expression. Hopefully, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form, independently from the equilibrium eigenvectors. Moreover, we can use it to extract the steady state by rising the vacuum state. We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$. 

>>>>

Since $Q^{2L}$ and $H^{''}$ are isospectral the above matrix $W$ still maps the non-equilibrium eigenvectors onto the equilibrium ones. The advantage is that now we can do more with the above expression. Firstly the eigenvalues $\Lambda_{\bm{m}}$ can be explicitly computed and secondly, using exchange relation between charges, we rewrite \eqref{WInCharges} in a better form that can be used to extract the steady state by rising the vacuum state. We first show the procedure in the $gl(2)$ case, and then we generalize it to arbitrary number of species $N$. 
